---
title: "Assignment2"
author: "Abdul Salaam Syed"
date: "3/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Part 1

*Abdul Salaam Syed*

## ID-s4602209 


<hr  style="border:5px solid"> 

# Assignment 2

<hr style="border:5px solid">

### Part 2
```{r}
library(tidyverse)
library(skimr)
install.packages("randomForest")
Data <-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")
```
### Answer 1
```{r}

knitr::kable(head(Data[,1:12],10))
```

### Answer 2
```{r}
Data1<-skim(Dataset)

```
### Answer 3
```{r}
family_income <-fct_reorder(Data$family_income, Dataset$family_income, min)
```
### Answer 4
```{r}
nrow(subset(Data, celebrate=='Yes'))
```
### Answer  5
```{r}
knitr::kable(Dataset %>% group_by(main_dish) %>%  count(main_prep) %>% arrange(desc(n)) %>% head(n=10))
```

### Answer 6
```{r}
Data %>% ggplot() +  aes(x = main_dish, fill = main_dish) +   geom_bar() + labs(x = "Main Dish", y = "Count", title = "Main dish served and method", subtitle = "Main Dish", caption = "main dish served with method",  fill = "Legend")
```


<p>Turkey the most prefered dish in all people. It is highly orderale item</p>
<br>

### Answer  7
```{r}
nrow(subset(Data, gravy=='Yes'))

nrow(subset(Sata, cranberry=='Canned' | cranberry=='Homemade'))

```
### Answer  8 and 9

```{r}
knitr::kable(Dataset %>% group_by(celebrate) %>%  count(family_income) %>% arrange(desc(n)) %>% head(n=10))
```
```{r}
Dataset %>% ggplot() +  aes(x = celebrate, fill =family_income) +   geom_bar() + labs(x = "celebrate", y = "Count", title = "Distribution W.R.T celebrate with income ranges", subtitle = "Celebrate", caption = "Distribution W.R.T. celebrate with income ranges",  fill = "Legend")
```
<p>The people preferences for enjoyment is highest and all the people wants to enjoy and participate in the party.</p>
<br>

### Answer 10
```{r}
Dataset1<-Data %>% select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))
```
<p>There are different filters are applied on the data using start with function. The results shows only those rows having highest relationships.</p>
<br>

### Answer  11 and 12
```{r}
library(widyr)
```
<p>Shows the correlation between different variables</p>
<br>
```{r}
Dataset1 %>% pairwise_cor(value, id, sort = TRUE)
```
<p>It shows the relationship and prepare the pair of variables so that relation between different variables can be developed.</p>
<br>
 
### Answer  13

```{r}
#regression model
Data_new <- do.call(data.frame, lapply(Data_new, function(x) {
  replace(x, is.infinite(x) | is.na(x) | is.nan(x), 0)
  })
)
#model1 
#model2
#model3
relationships <- lm(t(Data1[3])~t(Data1[5]),Data1)
summary(relationships)

relation <- lm(t(Data1[4])~t(Data1[6]),Data1)
summary(relationships)

relation <- lm(t(Data1[3])~t(Data1[5]),Data1)
summary(relationships)

```
<p>Different columns are selected for applying the model. All are showing different results. The best relationship is when linear regression is applied on the column family income </p>

<p> The best prediction model is linear regression. It develop the relationship between two variables and also identify the line equation for relationships</p>



